Multiresolution Neural Field Estimation

### 2011-03-01 Multiresolution_framework/ltx/manuscript.tex
free up some spaces

 \boldsymbol\upsilon_0&=\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}[\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf U]_{j,i}\\ 
 \boldsymbol\upsilon_1&=\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf U]_{j,i}\label{eq:upsilon1} \\

@@

\parham{where $[.]_{i,j}$ denotes $\left(i,j\right)^{th}$ (block) element of the (block) matrix. Each $1\times n_{\theta}$ block of the $n_x \times n_x$ block matrix}

@@

The histogram in \figurename{\ref{fig:ParametersHistogram}} demonstrates the performance of the parameter estimation. \dean{The results are good because the RMSE between the true and estimated kernels is $1.83$ (units?)... There is a bias of 7.4 \% in $\theta_1$ because..., which is not big deal.}
\begin{figure}[!h]
 \centering
 \includegraphics[scale=1]{./Graph/ObservationFreqResponse.pdf}
 \caption{(a) Mexican-hat connectivity kernel. The kernel is a composite of two B-spline
functions (dashed lines), representing local excitation and lateral inhibition. (b) The average (over time) power in dB of the spatial frequency of the observations. The dashed line shows the cutoff frequency (-3 dB point).}
\label{fig:KernelAndFreqResponse} 
  \end{figure} 
\begin{figure}[!h] 
 \centering
 \includegraphics[scale=1]{./Graph/Field.pdf}
 \caption{Actual (solid line) and estimated (dashed line) neural fields at a time instant for different spatial resolutions. (a) $j=0$, $n_x=17$. (b) $j=1$, $n_x=33$. (c) $j=2$, $n_x=65$. (d) $j=3$, $n_x=131$. (e) $j=4$, $n_x=263$.}
 \label{fig:FieldEstimates}
 \end{figure} 
\begin{figure}[!h] 
 \centering
 \includegraphics[scale=1]{./Graph/Hist.pdf}
 \caption{(a) RMSE of the estimated field at different spatial scales. (b-c) Histograms of the excitatory and inhibitory connectivity basis function parameter estimates, $\theta_0$ and $\theta_1$, respectively. The solid lines show the actual parameter values and the dotted lines show the means of the estimated parameters.}
 \label{fig:ParametersHistogram}
 \end{figure}

@@

  \newpage
% \bibliographystyle{unsrt} 
% \bibliography{MRAIDE}

>>>>

 \boldsymbol\upsilon_0 & =\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}[\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf U]_{j,i}\\ 
 \boldsymbol\upsilon_1 & =\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf U]_{j,i}\label{eq:upsilon1} \\

@@

where $[.]_{i,j}$ denotes $\left(i,j\right)^{th}$ (block) element of the (block) matrix. Each $1\times n_{\theta}$ block of the $n_x \times n_x$ block matrix.

@@

The histogram in \figurename{\ref{fig:ParametersHistogram}} demonstrates the performance of the parameter estimation. \dean{The results are good because the RMSE between the true and estimated kernels is $1.83$ (units?)... There is a bias of 7.4 \% in $\theta_1$ because..., which is not big deal.}
\begin{figure}[!h]
 \centering
 \includegraphics[scale=.9]{./Graph/ObservationFreqResponse.pdf}
 \caption{(a) Mexican-hat connectivity kernel. The kernel is a composite of two B-spline
functions (dashed lines), representing local excitation and lateral inhibition. (b) The average (over time) power in dB of the spatial frequency of the observations. The dashed line shows the cutoff frequency (-3 dB point).}
\label{fig:KernelAndFreqResponse} 
  \end{figure} 
\begin{figure}[!h] 
 \centering
 \includegraphics[scale=0.9]{./Graph/Field.pdf}
 \caption{Actual (solid line) and estimated (dashed line) neural fields at a time instant for different spatial resolutions. (a) $j=0$, $n_x=17$. (b) $j=1$, $n_x=33$. (c) $j=2$, $n_x=65$. (d) $j=3$, $n_x=131$. (e) $j=4$, $n_x=263$.}
 \label{fig:FieldEstimates}
 \end{figure} 
\begin{figure}[!h] 
 \centering
 \includegraphics[scale=1]{./Graph/Hist.pdf}
 \caption{(a) RMSE of the estimated field at different spatial scales. (b-c) Histograms of the excitatory and inhibitory connectivity basis function parameter estimates, $\theta_0$ and $\theta_1$, respectively. The solid lines show the actual parameter values and the dotted lines show the estimated parameters means.}
 \label{fig:ParametersHistogram}
 \end{figure}

@@

%   \newpage
% \bibliographystyle{unsrt} 
% \bibliography{MRAIDE}
